---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SOCcer

<!-- badges: start -->
[![R-CMD-check](https://github.com/dmolitor/SOCcer/workflows/R-CMD-check/badge.svg)](https://github.com/dmolitor/SOCcer/actions)
<!-- badges: end -->


The goal of SOCcer is to query the SOCcer API.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dmolitor/SOCcer")
```
## Example

This is a basic example of how to use the package:

```{r example}
library(SOCcer)
```

Using the built-in data set we can query the first three jobs and see how long
it takes.
```{r}
system.time({
  jobs <- soccer(
    job_title = job_desc$title[1:3],
    job_desc = job_desc$description[1:3],
    job_id = job_desc$job_id[1:3],
    n_results = 3,
    req_per_min = 12
  )
})
```

Now we can view the top 3 results for each posting.
```{r}
jobs
```

The API responses are stored locally in a persistent cache to keep duplicate
queries from hitting the API. As we can see, re-running the function returns
cached results and finishes almost immediately.
```{r}
system.time({
  jobs <- soccer(
    job_title = job_desc$title[1:3],
    job_desc = job_desc$description[1:3],
    job_id = job_desc$job_id[1:3],
    n_results = 3,
    req_per_min = 30
  )
})
```
